### 2021-04-07 ch07_conclusion/conclusion.tex
Fixed use of acronyms followed by non-whitespace

To overcome these issues of single-process-oriented emergent constraints,
\cref{ch:06:paper_gpp} introduces an alternative approach based on \ac{ML}.
This work is already published in \textcite{Schlund2020}. Since the new
technique relies on a large number of data points in order to train the \ac{ML}
algorithm, the scalar climate sensitivity expressed as \ac{ECS} or \ac{TCR} is
not an appropriate target variable. Therefore, this analysis does not focus on
reducing uncertainties in climate sensitivity itself but rather on a selected
process that contributes to it: \ac{GPP}. \Ac{GPP} is the largest flux of the
terrestrial carbon uptake and slows down global warming by removing \ac{CO2}
from the atmosphere. In the first step of the new two-step approach, a
published emergent constraint by \textcite{Wenzel2016} is used to constrain the
global mean \ac{GPP} at the end of the \nth{21} century in the \acs{CMIP}5
\acs{RCP}8.5 scenario to $\pmrangeunit{171}{12}{\GtCyr{}}$, compared to
unconstrained \acs{CMIP}5 model range of $\rangeunit{156}{247}{\GtCyr{}}$. This
first step corrects the \acs{CMIP}5 models' \ac{GPP} response to \ac{CO2},
which is primarily driven by the \ac{CO2} fertilization. In the second step, a
\ac{ML}-based climate model weighting approach is used to further constrain the
gridded \ac{GPP} based on present-day predictors that are relevant for the
simulation of \ac{GPP} in the \acp{ESM}. The \ac{ML} approach is mathematically
similar to the \ac{MDER} approach \autocite{Karpechko2013, Senftleben2020,
  Wenzel2016a}, but additionally considers multi-dimensional (gridded) target
variables and non-linear relationships between the predictors and the target
variables. A relationship between process-oriented predictors and future
projections of \ac{GPP} is established and then utilized to project today's
observed conditions into the future. The prediction phase of the new method can
be interpreted as an implicit performance weighting. However, due to the
complex structure of the used \ac{ML} algorithm (\ac{GBRT}) it is not possible
to extract specific values for the individual weights. Two target variables are
considered: the gridded monthly climatologies of absolute \ac{GPP}
(\range{2091}{2100}) and the gridded fractional \ac{GPP} change over the
\nth{21} century (2100 versus 2000). The latter quantity shows an increased
\acs{GPP} change in the high latitudes compared to regions closer to the
equator. The results of both approaches are consistent with each other and with
the global constraint of the first step. The new approach is validated by
comparing it to other statistical models (the \acs{CMIP}5 \ac{MMM} and a linear
\ac{LASSO} model) in a leave-one-model-out \ac{CV} setup. Compared to \ac{MMM}
(\ac{LASSO}), a reduction of the resulting mean \ac{RMSEP} of up to $48
\unit{\%}$ ($3 \unit{\%}$) is found when using the \ac{ML} approach. Moreover,
the evaluation of the global and local feature importance allows further
insights into the \ac{ML} model. For the first target variable (absolute
\ac{GPP}), historical \ac{GPP} is by far the most important predictor, which
can be explained with a correction of the historical bias in \ac{GPP} by the
new approach. For the second variable (fractional change in \ac{GPP}), \ac{T}
and \ac{LAI} are the most important features. A corresponding feature map shows
that \ac{T} dominates in the tropics and \ac{LAI} dominates in the northern
high latitudes, which might be attributed to an additional greening trend in
the high latitudes that enhances the \ac{GPP} increase in this region compared
to regions closer to the equator through an extension of the growing season.
This study directly addresses \cref{enum:01:question_3}
(\enquote{\KeyScienceQuestionThree{}}), which can be confidently answered with
\enquote{yes} based on the results found.

@@

A promising way forward to reduce uncertainties in multi-model climate
projections is to apply the new flexible \ac{ML}-based climate model weighting
approach introduced in \cref{ch:06:paper_gpp} to other target variables. While
the scalar metrics \ac{ECS} or \ac{TCR} with one value per climate model do not
offer enough training points for this technique, a possible alternative could
be the gridded \acl{T} over the \nth{21} century in the \ac{SSP} scenarios. A
relevant study in this context is given by \textcite{Brunner2020}, who use
performance- and interdependence-based climate model weighting to constrain the
\acl{T} over the \nth{21} century based on observable process-based predictors
of today's climate and which could serve as a possible baseline for the new
\ac{ML}-based weighting approach. An exciting and valuable addition to the
method could be causal inference \autocite{Nowack2020, Runge2019}. In the
current approach, the relationships between the different predictors and the
target variable are based on statistical correlation alone. Moreover, the local
feature importance maps do not reveal true causal relationships between the
predictors and the target variable, but only show the relative weight that is
given to a specific predictor at a specific location for the prediction of the
target variable by the \ac{ML} model. By integrating causal networks into the
new approach, it might be possible to explore and utilize true causal
connections instead.

The massive progress in \ac{AI} and \ac{ML} in recent years in combination with
ever increasing computational power and resources provided by modern
supercomputers has the potential for enormous improvements in climate modeling
and analysis \autocite{Reichstein2019}. Apart from the presented \ac{ML}-based
weighting approach, further possible applications of \ac{AI} and \ac{ML} in
climate science involve for example \ac{ML}-based parameterizations that are
learned from high-resolution climate models \autocite{Gentine2018, Rasp2018},
\ac{ML}-based analysis and prediction of forcing patterns \autocite{Barnes2019,
  Mansfield2020}, or learning of entire \acp{ESM} from observational products
\autocite{Geer2021}. Therefore, the foundation for innovative and
groundbreaking research in climate science for the near future has been laid,
which will help to further understand the Earth system and fight one of the
greatest challenges for humankind today: climate change.

>>>>

To overcome these issues of single-process-oriented emergent constraints,
\cref{ch:06:paper_gpp} introduces an alternative approach based on \ac{ML}.
This work is already published in \textcite{Schlund2020}. Since the new
technique relies on a large number of data points in order to train the \ac{ML}
algorithm, the scalar climate sensitivity expressed as \ac{ECS} or \ac{TCR} is
not an appropriate target variable. Therefore, this analysis does not focus on
reducing uncertainties in climate sensitivity itself but rather on a selected
process that contributes to it: \ac{GPP}. \Ac{GPP} is the largest flux of the
terrestrial carbon uptake and slows down global warming by removing \ac{CO2}
from the atmosphere. In the first step of the new two-step approach, a
published emergent constraint by \textcite{Wenzel2016} is used to constrain the
global mean \ac{GPP} at the end of the \nth{21} century in the \acs{CMIP}5
\acs{RCP}8.5 scenario to $\pmrangeunit{171}{12}{\GtCyr{}}$, compared to
unconstrained \acs{CMIP}5 model range of $\rangeunit{156}{247}{\GtCyr{}}$. This
first step corrects the \acs{CMIP}5 models' \ac{GPP} response to \ac{CO2},
which is primarily driven by the \ac{CO2} fertilization. In the second step, a
\acs{ML}-based climate model weighting approach is used to further constrain
the gridded \ac{GPP} based on present-day predictors that are relevant for the
simulation of \ac{GPP} in the \acp{ESM}. The \ac{ML} approach is mathematically
similar to the \ac{MDER} approach \autocite{Karpechko2013, Senftleben2020,
  Wenzel2016a}, but additionally considers multi-dimensional (gridded) target
variables and non-linear relationships between the predictors and the target
variables. A relationship between process-oriented predictors and future
projections of \ac{GPP} is established and then utilized to project today's
observed conditions into the future. The prediction phase of the new method can
be interpreted as an implicit performance weighting. However, due to the
complex structure of the used \ac{ML} algorithm (\ac{GBRT}) it is not possible
to extract specific values for the individual weights. Two target variables are
considered: the gridded monthly climatologies of absolute \ac{GPP}
(\range{2091}{2100}) and the gridded fractional \ac{GPP} change over the
\nth{21} century (2100 versus 2000). The latter quantity shows an increased
\acs{GPP} change in the high latitudes compared to regions closer to the
equator. The results of both approaches are consistent with each other and with
the global constraint of the first step. The new approach is validated by
comparing it to other statistical models (the \acs{CMIP}5 \ac{MMM} and a linear
\ac{LASSO} model) in a leave-one-model-out \ac{CV} setup. Compared to \ac{MMM}
(\ac{LASSO}), a reduction of the resulting mean \ac{RMSEP} of up to $48
\unit{\%}$ ($3 \unit{\%}$) is found when using the \ac{ML} approach. Moreover,
the evaluation of the global and local feature importance allows further
insights into the \ac{ML} model. For the first target variable (absolute
\ac{GPP}), historical \ac{GPP} is by far the most important predictor, which
can be explained with a correction of the historical bias in \ac{GPP} by the
new approach. For the second variable (fractional change in \ac{GPP}), \ac{T}
and \ac{LAI} are the most important features. A corresponding feature map shows
that \ac{T} dominates in the tropics and \ac{LAI} dominates in the northern
high latitudes, which might be attributed to an additional greening trend in
the high latitudes that enhances the \ac{GPP} increase in this region compared
to regions closer to the equator through an extension of the growing season.
This study directly addresses \cref{enum:01:question_3}
(\enquote{\KeyScienceQuestionThree{}}), which can be confidently answered with
\enquote{yes} based on the results found.

@@

A promising way forward to reduce uncertainties in multi-model climate
projections is to apply the new flexible \acs{ML}-based climate model weighting
approach introduced in \cref{ch:06:paper_gpp} to other target variables. While
the scalar metrics \ac{ECS} or \ac{TCR} with one value per climate model do not
offer enough training points for this technique, a possible alternative could
be the gridded \acl{T} over the \nth{21} century in the \ac{SSP} scenarios. A
relevant study in this context is given by \textcite{Brunner2020}, who use
performance- and interdependence-based climate model weighting to constrain the
\acl{T} over the \nth{21} century based on observable process-based predictors
of today's climate and which could serve as a possible baseline for the new
\acs{ML}-based weighting approach. An exciting and valuable addition to the
method could be causal inference \autocite{Nowack2020, Runge2019}. In the
current approach, the relationships between the different predictors and the
target variable are based on statistical correlation alone. Moreover, the local
feature importance maps do not reveal true causal relationships between the
predictors and the target variable, but only show the relative weight that is
given to a specific predictor at a specific location for the prediction of the
target variable by the \ac{ML} model. By integrating causal networks into the
new approach, it might be possible to explore and utilize true causal
connections instead.

The massive progress in \ac{AI} and \ac{ML} in recent years in combination with
ever increasing computational power and resources provided by modern
supercomputers has the potential for enormous improvements in climate modeling
and analysis \autocite{Reichstein2019}. Apart from the presented \acs{ML}-based
weighting approach, further possible applications of \ac{AI} and \ac{ML} in
climate science involve for example \acs{ML}-based parameterizations that are
learned from high-resolution climate models \autocite{Gentine2018, Rasp2018},
\acs{ML}-based analysis and prediction of forcing patterns
\autocite{Barnes2019, Mansfield2020}, or learning of entire \acp{ESM} from
observational products \autocite{Geer2021}. Therefore, the foundation for
innovative and groundbreaking research in climate science for the near future
has been laid, which will help to further understand the Earth system and fight
one of the greatest challenges for humankind today: climate change.
